Emory Cardiovscular Biobank

### 2021-08-19 Manuscript/03-Simulation.Rmd
Working on real_data analysis

```{r, fig.height=8}
targets::tar_load(binom_plot)
binom_plot
```

```{r, fig.height=8}
targets::tar_load(gaussian_plot)
gaussian_plot
```

```{r, fig.height=8}
targets::tar_load(poisson_plot)
poisson_plot
```

>>>>

```{r, fig.height=8, eval = FALSE}
targets::tar_load(binom_plot)
binom_plot
```

```{r, fig.height=8, eval = FALSE}
targets::tar_load(gaussian_plot)
gaussian_plot
```

```{r, fig.height=8, eval = FALSE}
targets::tar_load(poisson_plot)
poisson_plot
```

### 2021-08-19 Real_Data/Emory_Card_Biobank/Report.Rmd
Working on real_data analysis

train_dat <- targets::tar_read(RD_ECB_train_dat)
valid_dat <- targets::tar_read(RD_ECB_valid_dat)

gam_scn_res <- targets::tar_read(train_gam_screen)
```

@@

* Two data sets: model development set (N=`r NROW(train_dat)`), validation set (N=`r NROW(valid_dat)`)

@@

## Validation

The validation data set have mostly distinct feature from the training data set. Hence, the validation in the traditional sense does not exists.

```{r eval = F}

test_mz_names <- valid_dat  %>% select(starts_with("mz")) %>% names
measure.bh(mdl_defaul, new.x = test_sm_dat, new.y=valid_dat$death3yr)

measure.bh(mdl_dflt)
```

>>>>

train_dat <- targets::tar_read(RD_ECB_train_dat)
gam_scn_res <- targets::tar_read(train_gam_screen)
```

@@

* Two data sets: model development set (N=`r NROW(train_dat)`)

@@
